---
title: "calibration"
author: "Joyce Wu"
date: "`r Sys.Date()`"
output: word_document
---
The following results is varying the treatment initiation coverage between 2015 and 2022.  
```{r message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
# this script is for visulizing the calibraiton outcomes 
# once check the code is running then turn it to markdown file to output documents 
# although filename call calib_weight, but did not weight any transition btw subpops 


library(ggplot2)
library(ggrepel)
library(directlabels)
library(gridExtra)
library(grid)

project_name <- "POC_AU"

codefun_path <- paste("/Users/jjwu/Documents/Simplified-HCV-testing-model")

data_path <- paste("/Users/jjwu/Library/CloudStorage/OneDrive-UNSW/05. PhD Project/Simplified HCV testing model_/Projects/", 
                   project_name, sep = "")
# Load useful libraries

library("readr")
library("dplyr")
library("tidyr")
library("purrr")
library("parallel")
library("pacman")
library("doMC")

Rcode <- file.path(codefun_path, "03. Code")

DataFolder <- file.path(data_path, "01. DATA/model input" )

OutputFolder <- file.path(data_path, "02. Output")

load(file.path(OutputFolder, paste0(project_name, ".rda")))
load(file.path(OutputFolder, paste0(project_name, "cali.rda")))
load(file.path(OutputFolder, paste0(project_name, "cali_timev", ".rda")))

source(file.path(Rcode, "/Functions/plotFunctions.R")) 

# setting end Year 

endY <- 100
#### tidy up datapoint #### 

datapoint <- list()
datapoint[["N"]] <- 
  cbind.data.frame(year = rep(POC_AU$simY, length(POC_AU$popNames) +3), 
                   indicator = c(POC_AU$popNames, "Community", "Prison", "Total"), 
                   realpop = c(80000, 400000, 6993, 12696, 20311, 480000, 40000, 520000),
                   low= c(60000, 30000, 6163, 11819, 19332, 360000, 37314, 397314),
                   up = c(100000, 600000, 7869, 13525, 21292, 700000, 42686, 742686))

datapoint[["frac"]] <- 
  cbind.data.frame(year = rep(POC_AU$simY, 3), 
                   indicator = c("commu_proP_fit", "prison_proP_fit", 
                                 "prison_profP_fit"), 
                   realpop = c(16.67, 17.48, 31.74),
                   low= c(16.56, 17.11, 31.28),
                   up = c(16.77, 17.85, 32.7))

datapoint[["flow"]] <- 
  cbind.data.frame(year = rep(POC_AU$simY, 3), 
                   indicator = c("incar", "release", 
                                 "commu_stopinj"), 
                   realpop = c(63753, 63113, 5.4),
                   low= c(NA, NA, 4.3),
                   up = c(NA, NA, 6.7))



#### Result:population ####
#### N: each subpop/ total  #### 
# subpop as list
subpop_N <- lapply(POC_AU$popNames, function(x){ 
  
  a <- popResults_MidYear(POC_AU, calibrateInit,
                          Population = x,
                          Disease_prog = NULL, 
                          Cascade = NULL, param = NULL, 
                          endYear = endY)%>%ungroup()
})

names(subpop_N) <- POC_AU$popNames

# all subpop in one list 
pop_N <- dplyr::bind_rows(subpop_N, .id = 'population')

# total number 

total_N <- pop_N%>%group_by(year)%>%summarise(best = sum(best))

#### N: community ####
commu_N <- pop_N%>%filter(population %in% c("C_PWID", "C_fPWID"))%>%
  dplyr::group_by(year)%>%summarise_at("best",sum)

#### N: prison ####
prison_N <- pop_N%>%filter(population %in% c("P_PWID", "P_fPWID", "P_nPWID"))%>%
  dplyr::group_by(year)%>%summarise_at("best",sum)

#### N: prisonPWID ####
prisonPWID_N <- pop_N%>%filter(population %in% c("P_PWID", "P_fPWID"))%>%
  dplyr::group_by(year)%>%summarise_at("best",sum)

#### %: PWID in community/prison ####
commu_proP <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                    as.data.frame(pop_N[pop_N$population =="C_PWID",3] / commu_N[ ,-1])*100)%>%
  tibble::as_tibble()

prison_proP <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                     as.data.frame(pop_N[pop_N$population =="P_PWID",3] / prison_N[ ,-1])*100)%>%
  tibble::as_tibble()

#### % fPWID in prison #### 
prison_profP <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                      as.data.frame(pop_N[pop_N$population =="P_fPWID",3] / prison_N[ ,-1])*100)%>%
  tibble::as_tibble()



#### number of annual leaving in each subpop ####
# this is for getting annual number of released in non-PWID in prison 
rel <- indicatorResult_uno(POC_AU, calibrateInit, "newLeave",
                           populations = POC_AU$popNames, endYear= endY)%>%
  mutate(year = year + POC_AU$cabY - 1) 

#### number of annual entry model in each subpop ####
# to get the annual number of incarceration in non-PWID in prison 
entry <- indicatorResult_uno(POC_AU, calibrateInit, "newEntry",
                             populations = POC_AU$popNames, endYear= endY) %>%
  mutate(year = year + POC_AU$cabY - 1)



#### annual number of incarceration/release/injection relapse/ stopping injection #### 

PopTransition <- as.data.frame.table(calibrateInit$newpop_tran)%>%
  mutate(timestep = c(rep(seq(POC_AU$startYear, endY-POC_AU$timestep,
                              POC_AU$timestep),each = POC_AU$npops*POC_AU$npops)),
         from = Var1,
         To = Var2)%>%dplyr::select(-c(Var1, Var2, Var3))%>%
  filter(timestep != 1)
# giving the average number to first time step 
#impute <- PopTransition%>%filter(timestep >0 &timestep <2)%>%
#  group_by(from, To)%>%
#  mutate(total_pop = mean(Freq))%>%
#  dplyr::select(total_pop)%>%ungroup()

#impute <- impute[c(1:as.numeric(POC_AU$npops*POC_AU$npops)),]


#PopTransition[c(1:as.numeric(POC_AU$npops*POC_AU$npops)), "Freq"] <- impute$total_pop 

PopTransition_all <- cbind.data.frame(timestep = PopTransition$timestep, 
                                      from = PopTransition$from,  
                                      to = PopTransition$To, 
                                      best = PopTransition$Freq)%>%
  as_tibble()%>%
  mutate(year = c(rep(seq(POC_AU$startYear, endY - 2, 1), 
                      each = (1/POC_AU$timestep)*POC_AU$npops*POC_AU$npops),
                  rep(endY - 1 , each = (1/POC_AU$timestep -1)*POC_AU$npops*POC_AU$npops)))


PPTranTo <- PopTransition_all%>%
  group_by(year, from, to)%>%summarize(best = sum(best))

# incarceration 
incarce <- list()

incarce[["PWID"]] <- PPTranTo%>%filter(from == "C_PWID" & to == "P_PWID")

incarce[["fPWID"]] <- PPTranTo%>%filter(from == "C_fPWID" & to == "P_fPWID")

incarce_bind <- dplyr::bind_rows(incarce, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()%>%
  dplyr::select(year, population, best)

entry_nonPWID <- entry%>%filter(population =="P_nPWID") 

# total incarceration = incarceration in C_PWID + incarceration in C_fPWID + incarceration in non-PWID (entry:non-PWID)
incar_total <- rbind(incarce_bind, entry_nonPWID)%>%group_by(year)%>%
  summarize(best = sum(best))

# release 
release <- list()

release[["PWID"]] <- PPTranTo%>%filter(from == "P_PWID" & to == "C_PWID")

release[["fPWID"]] <- PPTranTo%>%filter(from == "P_fPWID" & to == "C_fPWID")

release_bind <- dplyr::bind_rows(release, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()%>%
  dplyr::select(year, population, best)

release_nonPWID <- rel%>%filter(population =="P_nPWID") 

release_total <- rbind(release_bind, release_nonPWID)%>%group_by(year)%>%
  summarize(best = sum(best))

# injection relapse 
inj_relap <- list()

inj_relap[["community"]] <- PPTranTo%>%filter(from == "C_fPWID" & to == "C_PWID")

inj_relap[["prison"]] <- PPTranTo%>%filter(from == "P_fPWID" & to == "P_PWID")

inj_relap_bind <- dplyr::bind_rows(inj_relap, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()


# stopping injection 
inj_stop <- list()

inj_stop[["community"]] <- PPTranTo%>%filter(from == "C_PWID" & to == "C_fPWID")

inj_stop[["prison"]] <- PPTranTo%>%filter(from == "P_PWID" & to == "P_fPWID")

inj_stop_bind <- dplyr::bind_rows(inj_stop, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()



####  incidence of stopping injecting #### 
inj_stop_inc <- list()

inj_stop_inc[["community"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(inj_stop[["community"]][ , "best"] / 
                        subpop_N[["C_PWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()


inj_stop_inc[["prison"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(inj_stop[["prison"]][ , "best"] / 
                        subpop_N[["P_PWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

inj_stop_inc_bind <- dplyr::bind_rows(inj_stop_inc, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()
####  incidence of injection relapse #### 
inj_relap_inc <- list()

inj_relap_inc[["community"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(inj_relap[["community"]][ , "best"] / 
                        subpop_N[["C_fPWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

inj_relap_inc[["prison"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(inj_relap[["prison"]][ , "best"] / 
                        subpop_N[["P_fPWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

inj_relap_inc_bind <- dplyr::bind_rows(inj_relap_inc, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()

#### incidence of incarceration  ####
incar_inc <- list()

incar_inc[["PWID"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                             as.data.frame(incarce[["PWID"]][ , "best"] / 
                                             subpop_N[["C_PWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

incar_inc[["fPWID"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                              as.data.frame(incarce[["fPWID"]][ , "best"] / 
                                              subpop_N[["C_fPWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

incar_inc_bind <- dplyr::bind_rows(incar_inc, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()

#### incidence of release  ####
release_inc <- list()

release_inc[["PWID"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(release[["PWID"]][ , "best"] / 
                        subpop_N[["P_PWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

release_inc[["fPWID"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(release[["fPWID"]][ , "best"] /
                        subpop_N[["P_fPWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

release_inc_bind <- dplyr::bind_rows(release_inc, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()

#==============================================================================#

#==============================================================================#


####Plot: population ####
#####plot: number of total pop  #####

totalPop_plot <- indicatorPlot(POC_AU, total_N, 
              ylabel = "Number (thousands)",
              xlimits = c(POC_AU$startYear, 
                          POC_AU$startYear+30, 5),
              calibration_Y = POC_AU$cabY,
              rangeun = NULL, 
              groupPlot = NULL, 
              facetPlot = NULL,
              observationData = NULL, 
              simulateYear = NULL) + theme_bw() +
  scale_y_continuous(limits = c(300000,825000), 
                     breaks = seq(300000,825000, 100000), 
                     labels = seq(300000,825000, 100000)/1000) + 
  ggtitle("Number of total population") + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Total", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), 
             colour = "black", shape = 5, size = 2)  + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Total", "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Total", "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1), 
        xend = (POC_AU$simY - POC_AU$cabY + 1)))
#####plot: number of pop in community/prison   #####
commuPop_plot <- indicatorPlot(POC_AU, commu_N, 
                          ylabel = "Number",
                          xlimits = c(POC_AU$startYear, 
                                      POC_AU$startYear+30, 5),
                          calibration_Y = POC_AU$cabY,
                          rangeun = NULL, 
                          groupPlot = NULL, 
                          facetPlot = NULL,
                          observationData = NULL, 
                          simulateYear = NULL) + theme_bw() +
  ggtitle("Number of total population") + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Community", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), 
    colour = "black", shape = 5, size = 2) + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Community", "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Community", "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1))) + 
  scale_y_continuous(limits = c(0,750000), breaks = seq(0, 750000, 50000)) 
  
prisonPop_plot <- indicatorPlot(POC_AU, prison_N, 
                               ylabel = "Number",
                               xlimits = c(POC_AU$startYear, 
                                           POC_AU$startYear + 30, 5),
                               calibration_Y = POC_AU$cabY,
                               rangeun = NULL, 
                               groupPlot = NULL, 
                               facetPlot = NULL,
                               observationData = NULL, 
                               simulateYear = NULL) + theme_bw() +
  ggtitle("Number of total population") + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Prison", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), 
    colour = "black", shape = 5, size = 2) + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Prison", "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Prison", "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1))) + 
  scale_y_continuous(limits = c(0,60000), breaks = seq(0, 60000, 10000))

##### plot: number of subpop ####
# sub pop full names 
Namelab <- c("PWID in community", "former PWID in community",
             "PWID in prison", "former PWID in prison", "non-PWID in prison")

subpop_N_plot <- list() 

for(x in seq_along(names(subpop_N))){ 
  
  subpop_N_plot[[x]] <- indicatorPlot(POC_AU, subpop_N[[x]] , 
                                      ylabel = "Number",
                                      xlimits = c(POC_AU$startYear, 
                                                  POC_AU$startYear + 30, 5),
                                      calibration_Y = POC_AU$cabY,
                                      rangeun = NULL, 
                                      groupPlot = NULL, 
                                      facetPlot = NULL,
                                      observationData = NULL, 
                                      simulateYear = NULL) +
    theme_bw() + ggtitle(paste0(Namelab[x])) 
    
}

subpop_N_plot[[1]] <- subpop_N_plot[[1]] + 
  scale_y_continuous(limits = c(0, 110000), breaks = seq(0, 110000, 5000)) + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[1], "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black", shape = 5, size = 2) + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[1], "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[1], "up"],         x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))

subpop_N_plot[[2]] <- subpop_N_plot[[2]] + 
  scale_y_continuous(limits = c(0, 700000), breaks = seq(0, 700000, 50000)) + 
  
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[2], "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black", shape = 5, size = 2) + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[2], "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[2], "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))

subpop_N_plot[[3]] <- subpop_N_plot[[3]] + 
  scale_y_continuous(limits = c(0, 15000), breaks = seq(0, 15000, 1000)) + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[3], "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black", shape = 5, size = 2) + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[3], "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[3], "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))
  

subpop_N_plot[[4]] <- subpop_N_plot[[4]] + 
  scale_y_continuous(limits = c(0, 50000), breaks = seq(0, 50000, 2000)) + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[4], "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black", shape = 5, size = 2) + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[4], "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[4], "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))

subpop_N_plot[[5]] <- subpop_N_plot[[5]] + 
  scale_y_continuous(limits = c(0, 25000), breaks = seq(0, 25000, 2500)) + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[5], "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black", shape = 5, size = 2) + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[5], "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[5], "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))



#####plot: % of PWID/fPWID in community/prison  ####
# P_PWID 
frac_PPWID_plot <- indicatorPlot(POC_AU, prison_proP , 
                                 ylabel = "Percentage (%)",
                                 xlimits = c(POC_AU$startYear, 
                                             POC_AU$startYear+30, 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeun = NULL, 
                                 groupPlot = NULL, 
                                 facetPlot = NULL,
                                 observationData = NULL, 
                                 simulateYear = NULL) + 
  theme_bw() + 
  scale_y_continuous(limits = c(0,20), breaks = seq(0, 20,5)) + ggtitle("PWID in prison")
frac_PPWID_plot <- frac_PPWID_plot + 
  geom_point(aes(
    y=datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "prison_proP_fit", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black", shape = 18) +
  geom_segment(
    aes(y = datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "prison_proP_fit", "low"], 
        yend = datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "prison_proP_fit", "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))
  
# P_fPWID
frac_PfPWID_plot <- indicatorPlot(POC_AU, prison_profP , 
                                 ylabel = "Percentage (%)",
                                 xlimits = c(POC_AU$startYear, 
                                             POC_AU$startYear+30, 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeun = NULL, 
                                 groupPlot = NULL, 
                                 facetPlot = NULL,
                                 observationData = NULL, 
                                 simulateYear = NULL) + 
  theme_bw() + 
  scale_y_continuous(limits = c(0,50), breaks = seq(0, 50,5)) + ggtitle("Former PWID in prison") + 
  geom_point(aes(
    y=datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "prison_profP_fit", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black",shape = 18) + 
  geom_segment(
    aes(y = datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "prison_profP_fit", "low"], 
        yend = datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "prison_profP_fit", "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))

# C_PWID 
frac_CPWID_plot <- indicatorPlot(POC_AU, commu_proP , 
                                  ylabel = "Percentage (%)",
                                  xlimits = c(POC_AU$startYear, 
                                              POC_AU$startYear+30, 5),
                                  calibration_Y = POC_AU$cabY,
                                  rangeun = NULL, 
                                  groupPlot = NULL, 
                                  facetPlot = NULL,
                                  observationData = NULL, 
                                  simulateYear = NULL) + 
  theme_bw() + 
  scale_y_continuous(limits = c(0,20), breaks = seq(0, 20,5)) + ggtitle("PWID in community")
  
frac_CPWID_plot <- frac_CPWID_plot + geom_point(aes(
    y=datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "commu_proP_fit", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black", shape= 5, size = 0.6) + 
  geom_segment(
    aes(y = datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "commu_proP_fit", "low"], 
        yend = datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "commu_proP_fit", "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))
  

#####plot: annual number entry to/release from prisons #### 
New_incar_plot <-  indicatorPlot(POC_AU, incar_total,
              ylabel = "Number",
              xlimits = c(POC_AU$cabY,
                          POC_AU$cabY+30, 5),
              calibration_Y = POC_AU$cabY,
              rangeu = NULL,
              groupPlot = NULL,
              facetPlot = NULL,
              observationData = NULL, 
              simulateYear = NULL) +
  ggtitle("Annual number entry prisons") + theme_bw() + 
  scale_y_continuous(limits = c(0, 75000), breaks = seq(0, 75000, 5000)) + 
  geom_point(aes(
    y=datapoint[["flow"]][datapoint[["flow"]][, "indicator"] == "incar", "realpop"], 
    x = POC_AU$simY ), colour = "black")

New_release_plot <-  indicatorPlot(POC_AU, release_total,
                                 ylabel = "Number",
                                 xlimits = c(POC_AU$cabY,
                                             POC_AU$cabY+30, 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeu = NULL,
                                 groupPlot = NULL,
                                 facetPlot = NULL,
                                 observationData = NULL, 
                                 simulateYear = NULL) +
  ggtitle("Annual number release from prisons") + theme_bw() + 
  scale_y_continuous(limits = c(0, 75000), breaks = seq(0, 75000, 5000)) + 
  geom_point(aes(
    y=datapoint[["flow"]][datapoint[["flow"]][, "indicator"] == "release", "realpop"], 
    x = POC_AU$simY ), colour = "black")

#####plot: annual number stopping/relapse injection ####
# stopping injection
New_stopinj_plot <-  indicatorPlot(POC_AU, inj_stop_bind,
                                 ylabel = "Number",
                                 xlimits = c(POC_AU$cabY,
                                             POC_AU$cabY+30, 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeu = NULL,
                                 groupPlot = NULL,
                                 facetPlot = population,
                                 observationData = NULL, 
                                 simulateYear = NULL) +
  ggtitle("Annual number stop injection") + theme_bw() + 
  scale_y_continuous(limits = c(0, 20000), breaks = seq(0, 20000, 5000)) 
# relapse injection
New_relapinj_plot <-  indicatorPlot(POC_AU, inj_relap_bind,
                                   ylabel = "Number",
                                   xlimits = c(POC_AU$cabY,
                                               POC_AU$cabY+30, 5),
                                   calibration_Y = POC_AU$cabY,
                                   rangeu = NULL,
                                   groupPlot = NULL,
                                   facetPlot = population,
                                   observationData = NULL, 
                                   simulateYear = NULL) +
  ggtitle("Annual number relapse injection") + theme_bw() + 
  scale_y_continuous(limits = c(0,2500), breaks = seq(0, 2500, 500)) 

##============================================================================##



#####plot: incidence of entry to/release from prisons #### 
Inc_incar_plot <- indicatorPlot(POC_AU,incar_inc_bind ,
                                 ylabel = "Incidence",
                                 xlimits = c(POC_AU$cabY,
                                             POC_AU$cabY+30, 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeu = NULL,
                                 groupPlot = NULL,
                                 facetPlot = population,
                                 observationData = NULL, 
                                 simulateYear = NULL) +
  ggtitle("Incidence of incarceration") + theme_bw() + 
  scale_y_continuous(limits = c(0, 20), breaks = seq(0, 20, 1)) 

Inc_release_plot <-  indicatorPlot(POC_AU, release_inc_bind,
                                   ylabel = "Incidence",
                                   xlimits = c(POC_AU$cabY,
                                               POC_AU$cabY+30, 5),
                                   calibration_Y = POC_AU$cabY,
                                   rangeu = NULL,
                                   groupPlot = NULL,
                                   facetPlot = population,
                                   observationData = NULL, 
                                   simulateYear = NULL) +
  ggtitle("Incidence of released") + theme_bw() + 
  scale_y_continuous(limits = c(0, 200), breaks = seq(0, 200, 10)) 

#####plot: incidence of stopping/relapse injection ####
# stopping injection
Inc_stopinj_plot <- list()


Inc_stopinj_plot <- lapply(inj_stop_inc, function(x){ 
  
  a <- indicatorPlot(POC_AU, x,
                     ylabel = "Incidence",
                     xlimits = c(POC_AU$startYear ,
                                 POC_AU$startYear+30, 5),
                     calibration_Y = POC_AU$cabY,
                     rangeu = NULL,
                     groupPlot = NULL,
                     facetPlot = NULL,
                     observationData = NULL, 
                     simulateYear = NULL) +
    ggtitle("Incidence of stop injection") + theme_bw() + 
    scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, 5))
  
  
  
  return(a)
   
})

Inc_stopinj_plot[["community"]] <-  Inc_stopinj_plot[["community"]] + 
  geom_point(aes(
    y=datapoint[["flow"]][datapoint[["flow"]][, "indicator"] == "commu_stopinj", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), 
    colour = "black") + 
    geom_segment(
      aes(y = datapoint[["flow"]][datapoint[["flow"]][, "indicator"] == "commu_stopinj", "low"], 
          yend = datapoint[["flow"]][datapoint[["flow"]][, "indicator"] == "commu_stopinj", "up"], 
          x = POC_AU$simY - POC_AU$cabY + 1, xend = POC_AU$simY - POC_AU$cabY + 1 )) + 
  scale_y_continuous(limits = c(0,20), breaks = seq(0, 20, 1))

  
  
# relapse injection
Inc_relapinj_plot <-  indicatorPlot(POC_AU, inj_relap_inc_bind,
                                    ylabel = "Incidence",
                                    xlimits = c(POC_AU$cabY,
                                                POC_AU$cabY+30, 5),
                                    calibration_Y = POC_AU$cabY,
                                    rangeu = NULL,
                                    groupPlot = NULL,
                                    facetPlot = population,
                                    observationData = NULL, 
                                    simulateYear = NULL) +
  ggtitle("Incidence of relapse injection") + theme_bw() + 
  scale_y_continuous(limits = c(0, 15), breaks = seq(0, 15, 1))

endY_plot <- 2030- POC_AU$cabY

#### Results: prevalence & incidence #### 
# Structure 
#####Prevalence#####
# (A)antibody prevalence 
#    (I) each subpop
#   (II) community
#   (III) Prison
#   (IV) Prison_f/PWID (P_fPWID, P_PWID)
# (B)RNA prevalence 
#    (I) each subpop
#   (II) community
#   (III) Prison
#   (IV) Prison_f/PWID (P_fPWID, P_PWID)

##### (A)antibody prevalence ##### 
#    (I) each subpop
# number of susceptible 
pop_state <- popResults_MidYear(POC_AU, calibrateInit,
                                             Population = POC_AU$popNames,
                                             Disease_prog = POC_AU$progress_name, 
                                             Cascade = POC_AU$cascade_name, param = NULL, 
                                             endYear = endY)%>%ungroup()%>%
  as_tibble()
  
tempNOTInfected_subpop <- pop_state%>%filter(disease_prog!= "a")%>%
  filter(state == "s")%>%group_by(year, population)%>%
  summarise(best = sum(best))%>%arrange(year, population)

tempChronic_subpop <- pop_state%>%filter(disease_prog!= "a")%>%
  group_by(year, population)%>%
  summarise(best = sum(best))%>%arrange(year, population)

# arrange order to align with other dts 
pop_N <- pop_N%>%arrange(year, population)


tempPrev_subpop <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), each = POC_AU$npops),
                         population = POC_AU$popNames,
                         
                         as.data.frame(100*(pop_N[, -c(1,2)] - 
                                              tempNOTInfected_subpop[ ,-c(1,2)])/ 
                                         pop_N[ ,-c(1,2)]))%>%
  tibble::as_tibble()  


#prevalence in setting  
# tempPrev_setting[["setting]]

# community 
commu_N <- commu_N%>%arrange(year)

tempNOTInfected_commu <- popResults_MidYear(POC_AU, calibrateInit,
                                            Population = c("C_PWID", "C_fPWID"),
                                             Disease_prog = NULL, 
                                             Cascade = c("s"), 
                                             param = NULL ,endYear = endY)%>%
  as_tibble()%>%group_by(year)%>%
  summarise(best = sum(best))%>%arrange(year)

tempPrev_setting <- list()

tempPrev_setting[["commu"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                                   as.data.frame(100*(commu_N[, -c(1)] - 
                                              tempNOTInfected_commu[ ,-c(1)])/ 
                                         commu_N[ ,-c(1)]))%>%tibble::as_tibble()

# prison 
## PWID + former PWID + nonPWID 
prison_N <- prison_N%>%arrange(year)

tempNOTInfected_prison <- popResults_MidYear(POC_AU, calibrateInit,
                                            Population = c("P_PWID", "P_fPWID", 
                                                           "P_nPWID"),
                                            Disease_prog = NULL, 
                                            Cascade = c("s"), 
                                            param = NULL ,endYear = endY)%>%
  as_tibble()%>%group_by(year)%>%
  summarise(best = sum(best))%>%arrange(year)


tempPrev_setting[["prisons"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                                     as.data.frame(100*(prison_N[, -c(1)] - 
                                                          tempNOTInfected_prison[ ,-c(1)])/ 
                                                     prison_N[ ,-c(1)]))%>%tibble::as_tibble()


# prison_PWID experienced  
## PWID + former PWID + nonPWID 
prisonPWID_N <- prisonPWID_N%>%arrange(year)

tempNOTInfected_prisonPWID <- popResults_MidYear(POC_AU, calibrateInit,
                                             Population = c("P_PWID", "P_fPWID"),
                                             Disease_prog = NULL, 
                                             Cascade = c("s"), 
                                             param = NULL ,endYear = endY)%>%
  as_tibble()%>%group_by(year)%>%
  summarise(best = sum(best))%>%arrange(year)


tempPrev_setting[["prisonsPWID"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                                       as.data.frame(100*(prisonPWID_N[, -c(1)] - 
                                                            tempNOTInfected_prisonPWID[ ,-c(1)])/ 
                                                       prisonPWID_N[, -c(1)]))%>%tibble::as_tibble()



##### (B)RNA prevalence ##### 
#    (I) each subpop
#   (II) community
#   (III) Prison
#   (IV) Prison_f/PWID (P_fPWID, P_PWID)
tempNOTInfectedRNA_subpop <- popResults_MidYear(POC_AU, calibrateInit,Population = POC_AU$popNames,
                                             Disease_prog = NULL, 
                                             Cascade = c("s", "cured"), 
                                             param = NULL ,endYear = endY)%>%
  as_tibble()%>%group_by(year, population)%>%
  summarise(best = sum(best))%>%arrange(year, population)



tempPrevRNA_subpop <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), each = POC_AU$npops),
                         population = POC_AU$popNames,
                         
                         as.data.frame(100*(pop_N[, -c(1,2)] - 
                                              tempNOTInfectedRNA_subpop[ ,-c(1,2)])/ 
                                         pop_N[ ,-c(1,2)]))%>%
  tibble::as_tibble()  


#prevalence in setting  
# tempPrev_setting[["setting]]


tempNOTInfectedRNA_commu <- popResults_MidYear(POC_AU, calibrateInit,
                                            Population = c("C_PWID", "C_fPWID"),
                                            Disease_prog = NULL, 
                                            Cascade = c("s", "cured"), 
                                            param = NULL ,endYear = endY)%>%
  as_tibble()%>%group_by(year)%>%
  summarise(best = sum(best))%>%arrange(year)

tempPrevRNA_setting <- list()

tempPrevRNA_setting[["commu"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                                     as.data.frame(100*(commu_N[, -c(1)] - 
                                                          tempNOTInfectedRNA_commu[ ,-c(1)])/ 
                                                     commu_N[ ,-c(1)]))%>%tibble::as_tibble()

# prison 
## PWID + former PWID + nonPWID 


tempNOTInfectedRNA_prison <- popResults_MidYear(POC_AU, calibrateInit,
                                             Population = c("P_PWID", "P_fPWID", 
                                                            "P_nPWID"),
                                             Disease_prog = NULL, 
                                             Cascade = c("s", "cured"), 
                                             param = NULL ,endYear = endY)%>%
  as_tibble()%>%group_by(year)%>%
  summarise(best = sum(best))%>%arrange(year)


tempPrevRNA_setting[["prisons"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                                       as.data.frame(100*(prison_N[, -c(1)] - 
                                                            tempNOTInfectedRNA_prison[ ,-c(1)])/ 
                                                       prison_N[ ,-c(1)]))%>%tibble::as_tibble()


# prison_PWID experienced  
## PWID + former PWID + nonPWID 


tempNOTInfectedRNA_prisonPWID <- popResults_MidYear(POC_AU, calibrateInit,
                                                 Population = c("P_PWID", "P_fPWID"),
                                                 Disease_prog = NULL, 
                                                 Cascade = c("s", "cured"), 
                                                 param = NULL ,endYear = endY)%>%
  as_tibble()%>%group_by(year)%>%
  summarise(best = sum(best))%>%arrange(year)


tempPrevRNA_setting[["prisonsPWID"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                                           as.data.frame(100*(prisonPWID_N[, -c(1)] - 
                                                                tempNOTInfectedRNA_prisonPWID[ ,-c(1)])/ 
                                                           prisonPWID_N[ ,-c(1)]))%>%tibble::as_tibble()



##### HCV incidence ##### 
HCVInfect_subpop <- indicatorResults(POC_AU, calibrateInit, "newInfections", 
                                     pop=POC_AU$popNames,
                                  paramR = NULL, range = NULL,
                                  endY = endY)

HCVInc_subpop <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), 
                                  each = POC_AU$npops),
                       population = POC_AU$popNames,
                       as.data.frame(100*HCVInfect_subpop[, -c(1,2)] / 
                                       pop_N[ ,-c(1,2)]))%>%
  tibble::as_tibble() 



HCVInfect_setting <- list()

HCVInfect_setting[["commu"]] <- indicatorResults(POC_AU, 
                                                     calibrateInit, 
                                                     "newInfections", 
                                                     pop= c("C_PWID", "C_fPWID"),
                                     paramR = NULL, range = NULL,
                                     endY = endY)%>%group_by(year)%>%
  summarise(best = sum(best))%>%arrange(year)

HCVInfect_setting[["prisons"]] <- indicatorResults(POC_AU, 
                                                   calibrateInit, 
                                                   "newInfections", 
                                                   pop= c("P_PWID", "P_fPWID",
                                                          "P_nPWID"), 
                                                   paramR = NULL, 
                                                   range = NULL,
                                                   endY = endY)%>%group_by(year)%>%
  summarise(best = sum(best))%>%arrange(year)

HCVInfect_setting[["prisonsPWID"]] <- indicatorResults(POC_AU, 
                                                   calibrateInit, 
                                                   "newInfections", 
                                                   pop= c("P_PWID", "P_fPWID"), 
                                                   paramR = NULL, 
                                                   range = NULL,
                                                   endY = endY)%>%group_by(year)%>%
  summarise(best = sum(best))%>%arrange(year)

HCVInc_setting <- list()

HCVInc_setting[["commu"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                                   as.data.frame(100*(HCVInfect_setting[["commu"]][ , -c(1)]/ 
                                                        commu_N[ ,-c(1)])))%>%
                                     tibble::as_tibble()
HCVInc_setting[["prisons"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                                   as.data.frame(100*(HCVInfect_setting[["prisons"]][ , -c(1)]/ 
                                                        prison_N[ ,-c(1)])))%>%
                                     tibble::as_tibble()


HCVInc_setting[["prisonsPWID"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                                   as.data.frame(100*(HCVInfect_setting[["prisonsPWID"]][ , -c(1)]/ 
                                                        prisonPWID_N[ ,-c(1)])))%>%
                                     tibble::as_tibble()


# primary infection 
##### HCV incidence ##### 
HCVInfectRE_subpop <- indicatorResults(POC_AU, calibrateInit, "newreinfection", 
                                     pop=POC_AU$popNames,
                                  paramR = NULL, range = NULL,
                                  endY = endY)

HCVIncp_subpop <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), 
                                  each = POC_AU$npops),
                       population = POC_AU$popNames,
                       as.data.frame(100*(HCVInfect_subpop[, -c(1,2)] - 
                                        HCVInfectRE_subpop[, -c(1,2)])/ 
                                       pop_N[ ,-c(1,2)]))%>%
  tibble::as_tibble() 


# reinfection

HCVIncre_subpop <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), 
                                  each = POC_AU$npops),
                       population = POC_AU$popNames,
                       as.data.frame(100*HCVInfectRE_subpop[, -c(1,2)]/ 
                                       pop_N[ ,-c(1,2)]))%>%
  tibble::as_tibble() 

####Plot: incidence and prevalence  ####
#####plot: prevalence #####
pop_labname <- c("PWID in community",  "Former PWID in community", 
                 "PWID in prisons",  "Former PWID in prisons", 
                 "nonPWID in prisons")
HCVPrev <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVPrev_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = HCV.seroprevalence*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))

tempPrev_subpop <- tempPrev_subpop%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname ))

popPrevPlot <- indicatorPlot(POC_AU, tempPrev_subpop, 
              ylabel = "HCV seroprevalence (%)",
              xlimits = c(POC_AU$startYear, 
                          (POC_AU$startYear+endY_plot), 5),
              calibration_Y = POC_AU$cabY,
              rangeun = NULL, 
              groupPlot = NULL, 
              facetPlot = population,
              observationData = HCVPrev, 
              simulateYear = POC_AU$simY) +
  ggtitle("HCV seroprevalence by population") 

popPrevPlot <- popPrevPlot + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 10)))
                   )) + theme_bw()

popPrevPlot 
# setting 
tempPrev_setting_bind <- dplyr::bind_rows(tempPrev_setting, .id = 'population')%>%
  mutate(population = factor(population, 
                             levels = c("commu", "prisons", "prisonsPWID"), 
                             labels = c("Community", "Prisons", 
                                        "Current & former PWID in prisons")))%>%
  as.data.frame()

HCVPrev_setting <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVPrev_setting_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = HCVPrev*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = c("commu", "prisons"), 
                                               labels = c("Community", "Prisons")))


settingPrevPlot <- indicatorPlot(POC_AU, tempPrev_setting_bind, 
                             ylabel = "HCV seroprevalence (%)",
                             xlimits = c(POC_AU$startYear, 
                                         (POC_AU$startYear+endY_plot - 1), 5),
                             calibration_Y = POC_AU$cabY,
                             rangeun = NULL, 
                             groupPlot = NULL, 
                             facetPlot = population,
                             observationData = HCVPrev_setting, 
                             simulateYear = POC_AU$simY) +
  ggtitle("HCV seroprevalence by setting") 

settingPrevPlot <- settingPrevPlot + 
  facet_custom (~population,
                scales = "free", ncol = 1,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 100)))
                    )) + theme_bw() 

##### B: RNA prevalence #####
tempPrevRNA_subpop <- tempPrevRNA_subpop%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname ))
HCVPrevRNA <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVPrevRNA_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = HCV.RNA.prevalence*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))
popPrevRNAPlot <- indicatorPlot(POC_AU, tempPrevRNA_subpop, 
                             ylabel = "HCV prevalence (%)",
                             xlimits = c(POC_AU$startYear, 
                                         (POC_AU$startYear+endY_plot), 5),
                             calibration_Y = POC_AU$cabY,
                             rangeun = NULL, 
                             groupPlot = NULL, 
                             facetPlot = population,
                             observationData = HCVPrevRNA , 
                             simulateYear = POC_AU$simY) +
  ggtitle("HCV RNA prevalence by population") 

popPrevRNAPlot <- popPrevRNAPlot + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 20)))
                  )) + theme_bw()

popPrevRNAPlot 
# setting 
tempPrevRNA_setting_bind <- dplyr::bind_rows(tempPrevRNA_setting, .id = 'population')%>%
  mutate(population = factor(population, 
                             levels = c("commu", "prisons", "prisonsPWID"), 
                             labels = c("Community", "Prisons", 
                                        "Current & former PWID in prisons")))%>%
  as.data.frame()

HCVPrevRNAsetting <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVPrevRNA_setting_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = HCVPrev*100,
                           low = lower*100,
                           up = upper*100,
                           population = factor(population, 
                                               levels = c("commu", "prisons"), 
                                               labels = c("Community", "Prisons" )))


settingPrevRNAPlot <- indicatorPlot(POC_AU, tempPrevRNA_setting_bind, 
                                 ylabel = "HCV RNA prevalence (%)",
                                 xlimits = c(POC_AU$startYear, 
                                             (POC_AU$startYear+endY_plot - 1), 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeun = NULL, 
                                 groupPlot = NULL, 
                                 facetPlot = population,
                                 observationData = HCVPrevRNAsetting, 
                                 simulateYear = POC_AU$simY) +
  ggtitle("HCV RNA prevalence by setting") 

settingPrevRNAPlot <- settingPrevRNAPlot + 
  facet_custom (~population,
                scales = "free", ncol = 1,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 100)))
                  )) + theme_bw()


settingPrevRNAPlot
#####plot: incidence #####
HCVInc_subpop <- HCVInc_subpop%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname )) 
# primary infection
HCVIncp_subpop <- HCVIncp_subpop%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname ))
# reinfection
HCVIncre_subpop <- HCVIncre_subpop%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname ))

HCVInc <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVInc_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = HCVInc*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))

HCVIncp <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVIncP_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = HCVInc,
                           up = upper,
                           low = lower,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))

HCVIncre <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVIncRe_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = HCVInc,
                           up = upper,
                           low = lower,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))

popIncPlot <- indicatorPlot(POC_AU, HCVInc_subpop, 
                             ylabel = "HCV incidence",
                             xlimits = c(POC_AU$startYear, 
                                         (POC_AU$startYear+endY_plot), 5),
                             calibration_Y = POC_AU$cabY,
                             rangeun = NULL, 
                             groupPlot = NULL, 
                             facetPlot = population,
                             observationData = HCVInc, 
                             simulateYear = POC_AU$simY) +
  ggtitle("HCV incidence by population") 

popIncPlot <- popIncPlot + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 25))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 25))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 40))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 25))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 10)))
                  )) + theme_bw()


popIncpPlot <- indicatorPlot(POC_AU, HCVIncp_subpop, 
                             ylabel = "HCV incidence",
                             xlimits = c(POC_AU$startYear, 
                                         (POC_AU$startYear+endY_plot), 5),
                             calibration_Y = POC_AU$cabY,
                             rangeun = NULL, 
                             groupPlot = NULL, 
                             facetPlot = population,
                             observationData = HCVIncp, 
                             simulateYear = POC_AU$simY) +
  ggtitle("HCV primary incidence by population") 

popIncpPlot <- popIncpPlot + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 25))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 25))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 75))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 50))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 10)))
                  )) + theme_bw()

popIncrePlot <- indicatorPlot(POC_AU, HCVIncre_subpop, 
                             ylabel = "HCV incidence",
                             xlimits = c(POC_AU$startYear, 
                                         (POC_AU$startYear+endY_plot), 5),
                             calibration_Y = POC_AU$cabY,
                             rangeun = NULL, 
                             groupPlot = NULL, 
                             facetPlot = population,
                             observationData = HCVIncre, 
                             simulateYear = POC_AU$simY) +
  ggtitle("HCV reinfection incidence by population") 

popIncrePlot <- popIncrePlot + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 10))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 10))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 25))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 25))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 100)))
                  )) + theme_bw()

# setting 
HCVInc_setting_bind <- dplyr::bind_rows(HCVInc_setting, .id = 'population')%>%
  mutate(population = factor(population, 
                             levels = c("commu", "prisons", "prisonsPWID"), 
                             labels = c("Community", "Prisons", 
                                        "Current & former PWID in prisons")))%>%
  as.data.frame()

HCVInc_setting_fit <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVInc_setting_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = HCVInc*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = c("commu", "prisons"), 
                                               labels = c("Community", "Prisons")))

settingIncPlot <- indicatorPlot(POC_AU, HCVInc_setting_bind, 
                                 ylabel = "HCV incidence",
                                 xlimits = c(POC_AU$startYear, 
                                             (POC_AU$startYear+endY_plot - 1), 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeun = NULL, 
                                 groupPlot = NULL, 
                                 facetPlot = population,
                                 observationData = HCVInc_setting_fit, 
                                 simulateYear = POC_AU$simY) +
  ggtitle("HCV incidence by setting") 

settingIncPlot <- settingIncPlot + 
    facet_custom (~population,
                  scales = "free", ncol = 1,
                  scale_overrides = 
                    list(
                      scale_new(1,
                                scale_y_continuous(limits = 
                                                     c(0, 25))),
                      scale_new(2,
                                scale_y_continuous(limits = 
                                                     c(0, 25))),
                       scale_new(3,
                                scale_y_continuous(limits = 
                                                     c(0, 25))))) + theme_bw()

####Results: death ####
#### HCV death ####

HCVdeath <- indicatorResults(POC_AU, calibrateInit, "newHCVdeaths", 
                            pop=POC_AU$popNames,
                            paramR = NULL, range = NULL,
                            endY = endY)%>%
  mutate(population = factor(population, 
                           levels = POC_AU$popNames, 
                           labels = pop_labname ))

death <- indicatorResults(POC_AU, calibrateInit, "newDeath", 
                          pop=POC_AU$popNames,
                          paramR = NULL, range = NULL,
                          endY = endY)%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname ))
  

HCVdeath_plot <- indicatorPlot(POC_AU, HCVdeath, 
              ylabel = "HCV-related deaths",
              xlimits = c(POC_AU$startYear, 
                          (POC_AU$startYear+endY_plot), 5),
              calibration_Y = POC_AU$cabY,
              rangeun = NULL, 
              groupPlot = NULL, 
              facetPlot = population,
              observationData = NULL, 
              simulateYear = POC_AU$simY) +
  ggtitle("HCV-related deaths") + theme_bw()


HCVdeath_plot <- HCVdeath_plot + 
  facet_custom(~population,
               scales = "free", ncol = 3,
               scale_overrides = 
                 list(
                   scale_new(1,
                             scale_y_continuous(limits = 
                                                  c(0, 100))),
                   scale_new(2,
                             scale_y_continuous(limits = 
                                                  c(0, 500))),
                   scale_new(3,
                             scale_y_continuous(limits = 
                                                  c(0, 20))),
                   scale_new(4,
                             scale_y_continuous(limits = 
                                                  c(0, 20))),
                   scale_new(5,
                             scale_y_continuous(limits = 
                                                  c(0, 5))))) 

death_plot <- indicatorPlot(POC_AU, death, 
                               ylabel = "Deaths",
                               xlimits = c(POC_AU$startYear, 
                                           (POC_AU$startYear+endY_plot), 5),
                               calibration_Y = POC_AU$cabY,
                               rangeun = NULL, 
                               groupPlot = NULL, 
                               facetPlot = population,
                               observationData = NULL, 
                               simulateYear = POC_AU$simY) +
  ggtitle("Deaths") 


death_plot <- death_plot + 
  facet_custom(~population,
               scales = "free", ncol = 3,
               scale_overrides = 
                 list(
                   scale_new(1,
                             scale_y_continuous(limits = 
                                                  c(0, 2000))),
                   scale_new(2,
                             scale_y_continuous(limits = 
                                                  c(0, 10000))),
                   scale_new(3,
                             scale_y_continuous(limits = 
                                                  c(0, 1000))),
                   scale_new(4,
                             scale_y_continuous(limits = 
                                                  c(0, 500))),
                   scale_new(5,
                             scale_y_continuous(limits = 
                                                  c(0, 5))))) 

#### Results: all component ####
pop_state <- popResults_MidYear(POC_AU, calibrateInit,
                                 Population = POC_AU$popNames,
                                 Disease_prog = POC_AU$progress_name, 
                                 Cascade = POC_AU$cascade_name, param = NULL, 
                                 endYear = endY)%>%ungroup()

pop_stateAll <- pop_state%>%group_by(year, state)%>%
  summarise_at("best",sum)

pop_stateSub <- pop_state%>%group_by(year, population, state)%>%
  summarise_at("best", sum)

# plot 
Ppop_stateAll <-  ggplot(data = pop_stateAll, aes(x = year, y = best)) + 
  geom_area() + 
  facet_wrap(.~ state, scale = "free") + 
  labs(y = "Number") + 
  scale_x_continuous( 
    limits = c(1, 31), 
    breaks = seq(1,31, 5),
    labels = seq(POC_AU$cabY,POC_AU$cabY + 30, 5)) 

#### Results: disease progression ####

pop_dispro <- popResults_MidYear(POC_AU, calibrateInit,
                        Population = POC_AU$popNames,
                        Disease_prog = POC_AU$progress_name, 
                        Cascade = NULL, param = NULL, 
                        endYear = endY)%>%ungroup()

pop_disproAll <- pop_dispro%>%group_by(year, disease_prog)%>%
  summarise_at("best",sum)

pop_disproSub <- pop_dispro%>%group_by(year, population, disease_prog)%>%
  summarise_at("best", sum)

# tidy up the code for presenting plot 
#  Area plot 
## disease_prog by order 

Ppop_disproAll <- ggplot(data = pop_disproAll, aes(x = year, y = best,group)) + 
  geom_area(aes(fill = disease_prog)) + 
  scale_x_continuous( 
                     limits = c(1, 31), 
                     breaks = seq(1,31, 5),
                     labels = seq(POC_AU$cabY,POC_AU$cabY + 30, 5))
 
#### Results: Cascade ####
pop_casca <- popResults_MidYear(POC_AU, calibrateInit,
                                 Population = POC_AU$popNames,
                                 Disease_prog = NULL, 
                                 Cascade = POC_AU$cascade_name, 
                                 param = NULL, 
                                 endYear = endY)%>%ungroup()

pop_cascaAll <- pop_casca%>%group_by(year, cascade)%>%
  summarise_at("best",sum)

pop_cascaSub <- pop_casca%>%group_by(year, population, cascade)%>%
  summarise_at("best", sum)

Ppop_cascaAll <- ggplot(data = pop_cascaAll, aes(x = year, y = best,group)) + 
  geom_area(aes(fill = cascade)) + 
  scale_x_continuous( 
    limits = c(1, 31), 
    breaks = seq(1,31, 5),
    labels = seq(POC_AU$cabY,POC_AU$cabY + 30, 5))


#### flow
# select flow outcomes from the output list 
calibrateFlow <- calibrateInit[!names(calibrateInit)%in%
                      c("allPops", "newpop_tran", "newpop_tranState", "HCVdeathState",
                      "newDeathState", "death_hcv")]

flow_sub <- list()
flow_all <- list()

flow_sub <- lapply(names(calibrateFlow), function(x){ 
  a <- indicatorResults(POC_AU, calibrateFlow, x, 
                        pop=POC_AU$popNames,
                        paramR = NULL, range = NULL,
                        endY = endY)
  })

names(flow_sub) <- names(calibrateFlow)

flow_all <- lapply(flow_sub, function(x){ 
  
  a <- x%>%group_by(year)%>%summarise_at("best", sum)
  }) 

names(flow_all) <- names(calibrateFlow)

# plot for flow 
pflow_all <- list()
pflow_all <- lapply(names(flow_all), function(x){ 

  a <- indicatorPlot(POC_AU, flow_all[[x]], 
                     ylabel = "Numbers",
                     xlimits = c(POC_AU$startYear, 
                                 (POC_AU$startYear+endY_plot), 5),
                     calibration_Y = POC_AU$cabY,
                     rangeun = NULL, 
                     groupPlot = NULL, 
                     facetPlot = NULL,
                     observationData = NULL, 
                     simulateYear = POC_AU$simY) +
    ggtitle(x) + theme_Publication()
  
  a <- a + expandy_man(flow_all[[x]], POC_AU$startYear+endY_plot)
  
  return(a)
  })

names(pflow_all) <- names(flow_all)


pflow_sub <- lapply(names(flow_sub), function(x){ 
  
  a <- indicatorPlot(POC_AU, flow_sub[[x]], 
                     ylabel = "Numbers",
                     xlimits = c(POC_AU$startYear, 
                                 (POC_AU$startYear+endY_plot), 5),
                     calibration_Y = POC_AU$cabY,
                     rangeun = NULL, 
                     groupPlot = NULL, 
                     facetPlot = population,
                     observationData = NULL, 
                     simulateYear = POC_AU$simY) +
    ggtitle(x)
  
})

names(pflow_sub) <- names(flow_sub)

#cascade ab
## calibration datasets 
HCVab <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVAbtest_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = abCoverage*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))

HCVrna <- read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVRNAtest_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = RNACoverage*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))

HCVrnaonly <- read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVRNAonlytest_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = RNAonlyCoverage*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))


HCVTinit <- read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVTinit_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = abCoverage*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))

# newtestingab/chronic infected + cured from chronic stage 
testab <- pop_stateSub%>%
  filter(state%in% c("f0_undiag", "f1_undiag", "f2_undiag", "f3_undiag",
                     "f4_undiag", "dc_undiag", "hcc_undiag", "lt_undiag",
                     "plt_undiag"))%>%
  group_by(year,population)%>%
  summarize(best = sum(best))




Tab_frag <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), 
                             each = POC_AU$npops),
                  population = POC_AU$popNames,
                  as.data.frame(100*flow_sub$newTestingAb[, -c(1,2)] / 
                                  testab[ ,-c(1,2)]))%>%
  tibble::as_tibble()%>%
  mutate(population = factor(population, 
                levels = POC_AU$popNames, 
                labels = pop_labname ))
  

Tpoct_frag <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), 
                             each = POC_AU$npops),
                  population = POC_AU$popNames,
                  as.data.frame(100*flow_sub$newTestingPOCT[, -c(1,2)] / 
                                  testab[ ,-c(1,2)]))%>%
  tibble::as_tibble()%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname ))

testrna <- pop_stateSub%>%
  filter(state%in% c("f0_diag_ab", "f1_diag_ab", "f2_diag_ab", "f3_diag_ab",
                     "f4_diag_ab", "dc_diag_ab", "hcc_diag_ab", "lt_diag_ab",
                     "plt_diag_ab"))%>%
  group_by(year,population)%>%
  summarize(best = sum(best))

Trna_frag <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), 
                               each = POC_AU$npops),
                    population = POC_AU$popNames,
                    as.data.frame(100*flow_sub$newTestingAg[, -c(1,2)] / 
                                    testrna[ ,-c(1,2)]))%>%
  tibble::as_tibble()%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname ))

treatint <- pop_stateSub%>%
  filter(state%in% c("a_diag_RNA", "f0_diag_RNA", "f1_diag_RNA", "f2_diag_RNA", "f3_diag_RNA",
                     "f4_diag_RNA", "dc_diag_RNA", "hcc_diag_RNA", "lt_diag_RNA",
                     "plt_diag_RNA"))%>%
  group_by(year,population)%>%
  summarize(best = sum(best))

Tint_frag <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), 
                              each = POC_AU$npops),
                   population = POC_AU$popNames,
                   as.data.frame(100*flow_sub$newTreatment[, -c(1,2)] / 
                                   treatint[ ,-c(1,2)]))%>%
  tibble::as_tibble()%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname ))

Tab_frag_p <- indicatorPlot(POC_AU, Tab_frag, 
                             ylabel = "%",
                             xlimits = c(POC_AU$startYear, 
                                         (POC_AU$startYear+endY_plot), 5),
                             calibration_Y = POC_AU$cabY,
                             rangeun = NULL, 
                             groupPlot = NULL, 
                             facetPlot = population,
                             observationData = HCVab, 
                             simulateYear = POC_AU$simY) + 
  ggtitle("antibody testing coverage") 

Tab_frag_p <- Tab_frag_p + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 40))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 40))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 80))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 40))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 20)))
                  )) + theme_bw()

Tpoct_frag_p <- indicatorPlot(POC_AU, Tpoct_frag, 
                            ylabel = "%",
                            xlimits = c(POC_AU$startYear, 
                                        (POC_AU$startYear+endY_plot), 5),
                            calibration_Y = POC_AU$cabY,
                            rangeun = NULL, 
                            groupPlot = NULL, 
                            facetPlot = population,
                            observationData = HCVrnaonly, 
                            simulateYear = POC_AU$simY) + 
  ggtitle("point-of-care RNA testing coverage")

Tpoct_frag_p <- Tpoct_frag_p + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 40))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 40))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 30))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 40))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 20)))
                  )) + theme_bw()
  

Trna_frag_p <- indicatorPlot(POC_AU, Trna_frag, 
              ylabel = "%",
              xlimits = c(POC_AU$startYear, 
                          (POC_AU$startYear+endY_plot), 5),
              calibration_Y = POC_AU$cabY,
              rangeun = NULL, 
              groupPlot = NULL, 
              facetPlot = population,
              observationData = HCVrna, 
              simulateYear = POC_AU$simY) + 
  ggtitle("RNA testing coverage") 

Trna_frag_p <- Trna_frag_p + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 100)))
                  )) + theme_bw()

Tint_frag_p <- indicatorPlot(POC_AU, Tint_frag, 
                             ylabel = "%",
                             xlimits = c(POC_AU$startYear, 
                                         (POC_AU$startYear+endY_plot), 5),
                             calibration_Y = POC_AU$cabY,
                             rangeun = NULL, 
                             groupPlot = NULL, 
                             facetPlot = population,
                             observationData = HCVTinit, 
                             simulateYear = POC_AU$simY) + 
  ggtitle("Percentage of treatment init") 

Tint_frag_p <- Tint_frag_p + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 100)))
                  )) + theme_bw()
  

### treatment init 

# lifetime treatment init in C_PWID 


# treatment init annual numbers in prisons from 2016 to 2022 

pflow_sub$newTreatment + theme_bw()

# by setting 
flow_setting <- lapply(flow_sub, function(x){ 
  
  a <- x%>%
    mutate(setting = ifelse(population %in% c("C_PWID", "C_fPWID"), 
                            "commu", "prisons"))
  
  a <- a%>%group_by(year, setting)%>%summarise_at("best", sum)%>%
    mutate(population = setting)%>%select(-setting)
}) 
N_treatment <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), 
                                each = 2),
                     population = flow_setting$newTreatment[ ,3],
                     as.data.frame(flow_setting$newTreatment[, -c(1,3)] + 
                                     flow_setting$newRetreat[, -c(1,3)] ))%>%
  tibble::as_tibble()%>%
  mutate(population = factor(population, 
                             levels = c("commu", "prisons"), 
                             labels = c("Community", "Prisons" )))



HCVtreatinitN_setting_fit <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVtreatinitN_setting_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = realpop,
                           up = upper,
                           low = lower,
                           population = factor(population, 
                                               levels = c("commu", "prisons"), 
                                               labels = c("Community", "Prisons")))
N_treatment$population

N_treatment_setting_p <- indicatorPlot(POC_AU, N_treatment, 
              ylabel = "N",
              xlimits = c(POC_AU$startYear, 
                          (POC_AU$startYear+endY_plot), 5),
              calibration_Y = POC_AU$cabY,
              rangeun = NULL, 
              groupPlot = NULL, 
              facetPlot = population,
              observationData = HCVtreatinitN_setting_fit, 
              simulateYear = POC_AU$simY) + 
  ggtitle("Number of treatment init") + theme_bw()

N_treatment_setting_p <- N_treatment_setting_p + 
  facet_custom (~population,
                scales = "free", ncol = 2,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 40000))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 5000)))))
N_treatment_setting_p


# lifetime treatment initated 
HCVtreatever <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVtreatever_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = realpop*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))



Tever <- pop_state%>%
  filter(cascade %in% c("treat", "treat_f", "cured") & disease_prog!= "a")%>%
  group_by(year, population)%>%summarise(best = sum(best))
HCVever <- pop_state%>%
  filter(!disease_prog%in% c ("s", "a"))%>%
  group_by(year, population)%>%summarise(best = sum(best))

treatInit_ever <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), 
                 each = POC_AU$npops),
      population = POC_AU$popNames,
      as.data.frame(100*Tever[, -c(1,2)] / 
                      HCVever[ ,-c(1,2)]))%>%
  tibble::as_tibble()%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname ))

treatInit_ever_p <- indicatorPlot(POC_AU, treatInit_ever, 
                                  ylabel = "%",
                                  xlimits = c(POC_AU$startYear, 
                                              (POC_AU$startYear+endY_plot), 5),
                                  calibration_Y = POC_AU$cabY,
                                  rangeun = NULL, 
                                  groupPlot = NULL, 
                                  facetPlot = population,
                                  observationData = HCVtreatever, 
                                  simulateYear = POC_AU$simY) + 
  ggtitle("Lifetime treatment initiated") 

treatInit_ever_p <- treatInit_ever_p + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 100)))
                  )) + theme_bw()
treatInit_ever_p


# prevalence of treat in the previous y: number of initiated treatment in the previosu year/ total pop

Prevtreatinit_subpop <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), 
                                  each = POC_AU$npops),
                       population = POC_AU$popNames,
                       as.data.frame((flow_sub$newTreatment[, -c(1,2)] + 
                                        flow_sub$newRetreat[, -c(1,2)]) / 
                                       pop_N[ ,-c(1,2)]*100))%>%
  tibble::as_tibble()%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname ))


treatrecentPrev <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVtreatrecentPrev_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = realpop*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))

treatrecentPrev_p <- indicatorPlot(POC_AU, Prevtreatinit_subpop, 
                                  ylabel = "%",
                                  xlimits = c(POC_AU$startYear, 
                                              (POC_AU$startYear+endY_plot), 5),
                                  calibration_Y = POC_AU$cabY,
                                  rangeun = NULL, 
                                  groupPlot = NULL, 
                                  facetPlot = population,
                                  observationData = treatrecentPrev, 
                                  simulateYear = POC_AU$simY) + 
  ggtitle("treatment initiated in the past year among population") 

treatrecentPrev_p  <- treatrecentPrev_p  + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 100)))
                  )) + theme_bw()
treatrecentPrev_p 


# recent treatment: flow of new treatment + flow of new retreatment /(diagRNA + treatint + treat_f + flow_SVR)
Trecent <- pop_state%>%
  filter(cascade %in% c("treat", "treat_f", "diag_RNA") & disease_prog!= "a")%>%
  group_by(year, population)%>%summarise(best = sum(best))



treatrecent_subpop <- cbind(year = rep(seq(POC_AU$startYear , endY-1 ,1), 
                                  each = POC_AU$npops),
                       population = POC_AU$popNames,
                       as.data.frame(100*(flow_sub$newTreatment[, -c(1,2)] + 
                                        flow_sub$newRetreat[, -c(1,2)]) / 
                                       (flow_sub$newCured[, -c(1,2)] + Trecent[ ,-c(1,2)])))%>%
  tibble::as_tibble()%>%
  mutate(population = factor(population, 
                             levels = POC_AU$popNames, 
                             labels = pop_labname ))


treatrecent_fit <-read.csv(file.path(paste0(DataFolder%>%dirname(), "/HCVtreatrecent_POC_AU.csv")), header = TRUE)%>%
  as.data.frame()%>%mutate(time = year- POC_AU$cabY + 1, 
                           realPop = realpop*100,
                           up = upper*100,
                           low = lower*100,
                           population = factor(population, 
                                               levels = POC_AU$popNames, 
                                               labels = pop_labname ))

treatrecent_p <- indicatorPlot(POC_AU, treatrecent_subpop, 
                                  ylabel = "%",
                                  xlimits = c(POC_AU$startYear, 
                                              (POC_AU$startYear+endY_plot), 5),
                                  calibration_Y = POC_AU$cabY,
                                  rangeun = NULL, 
                                  groupPlot = NULL, 
                                  facetPlot = population,
                                  observationData = treatrecent_fit, 
                                  simulateYear = POC_AU$simY) + 
  ggtitle("treatment initiated in the past year among people diagnosed with HCV") + 
  labs(caption = "Excludes people who reported treatment induced clearance more than 12 months previously")

treatrecent_p  <- treatrecent_p  + 
  facet_custom (~population,
                scales = "free", ncol = 3,
                scale_overrides = 
                  list(
                    scale_new(1,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(2,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    
                    scale_new(3,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(4,
                              scale_y_continuous(limits = 
                                                   c(0, 100))),
                    scale_new(5,
                              scale_y_continuous(limits = 
                                                   c(0, 100)))
                  )) + theme_bw()
treatrecent_p 


# check 

ggpubr::ggarrange(plotlist = subpop_N_plot) 
popPrevPlot
popPrevRNAPlot
settingPrevPlot
settingPrevRNAPlot
settingIncPlot
popIncPlot
Tab_frag_p
Tpoct_frag_p
Trna_frag_p
Tint_frag_p
treatInit_ever_p
N_treatment_setting_p
treatrecentPrev_p 
treatrecent_p 
```

```{r message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}

x <- indicatorResults(POC_AU, calibrateInit, "newTreatment", 
                      pop=POC_AU$popNames,
                      paramR = NULL, range = NULL,
                      endY = 100)

x_re <- indicatorResults(POC_AU, calibrateInit, "newRetreat", 
                         pop=POC_AU$popNames,
                         paramR = NULL, range = NULL,
                         endY = 100)



df_allpop <-calibrateInit$allPops%>%as.data.frame.table()%>%
  mutate(time = rep(seq(1.0,(100 - POC_AU$timestep), POC_AU$timestep), 
                    each=POC_AU$ncomponent*POC_AU$npops),
         cascade = sub("^[^_]*_", "", Var2), 
         disease_prog = sub("\\_.*", "", Var2))%>%
  dplyr::select(-Var3)%>%ungroup()%>%
  group_by(time, Var1, cascade)%>%
  summarise(Freq = sum(Freq))

df_diag <- df_allpop%>%filter(cascade == "diag_RNA")
df_undiag <- df_allpop%>%filter(cascade == "undiag")
df_diagab <- df_allpop%>%filter(cascade == "diag_ab")
df_undiag$Freq
newT <- calibrateInit$newTreatment%>%as.data.frame.table()%>%
  mutate(time = rep(seq(1.0,(100 - POC_AU$timestep), POC_AU$timestep), 
                    each=POC_AU$npops))

newdab <- calibrateInit$newTestingAb%>%as.data.frame.table()%>%
  mutate(time = rep(seq(1.0,(100 - POC_AU$timestep), POC_AU$timestep), 
                    each=POC_AU$npops))
newdRNA <- calibrateInit$newTestingAg%>%as.data.frame.table()%>%
  mutate(time = rep(seq(1.0,(100 - POC_AU$timestep), POC_AU$timestep), 
                    each=POC_AU$npops))

newdRNAonly <- calibrateInit$newTestingPOCT%>%as.data.frame.table()%>%
  mutate(time = rep(seq(1.0,(100 - POC_AU$timestep), POC_AU$timestep), 
                    each=POC_AU$npops))

ab_frac <- cbind(time = newdab$time, population = newdab$Var1, 
                               dab_n = newdab$Freq, 
                               Diag_n = df_undiag$Freq)%>%as_tibble()%>%
  mutate(Tinit_frac = 100*dab_n/Diag_n)

RNA_frac <- cbind(time = newdRNA$time, population = newdRNA$Var1, 
                 dab_n = newdRNA$Freq, 
                 Diag_n = df_diagab$Freq)%>%as_tibble()%>%
  mutate(Tinit_frac = 100*dab_n/Diag_n)

RNAonly_frac <- cbind(time = newdRNAonly$time, population = newdRNAonly$Var1, 
                  dab_n = newdRNAonly$Freq, 
                  Diag_n = df_undiag$Freq)%>%as_tibble()%>%
  mutate(Tinit_frac = 100*dab_n/Diag_n)

P_abFrac <- ggplot(ab_frac%>%filter(time!=1), aes(x = time, y = Tinit_frac)) + 
  geom_line() +
  facet_wrap(.~ population, scales = "free") + 
  scale_y_continuous(limits = c(0, 10)) + 
  ggtitle("ab") + labs(y = "ab testing %")

P_RNAFrac <- ggplot(RNA_frac%>%filter(time!=1), aes(x = time, y = Tinit_frac)) + 
  geom_line() +
  facet_wrap(.~ population, scales = "free") + 
  scale_y_continuous(limits = c(0, 10)) + 
  ggtitle("RNA") + labs(y = "RNA testing %")

P_RNAonlyFrac <- ggplot(RNAonly_frac%>%filter(time!=1), aes(x = time, y = Tinit_frac)) + 
  geom_line() +
  facet_wrap(.~ population, scales = "free") + 
  scale_y_continuous(limits = c(0, 5)) + 
  ggtitle("RNAonly") + labs(y = "test RNA only %")

30/12
# treatment coverage 
Tinit_frac <- cbind(time = newT$time, population = newT$Var1, 
                    Tinit_n = newT$Freq, 
                    Diag_n = df_diag$Freq)%>%as_tibble()%>%
  mutate(Tinit_frac = 100*Tinit_n/Diag_n)

P_TinitFrac <- ggplot(Tinit_frac%>%filter(time!=1), aes(x = time, y = Tinit_frac)) + 
  geom_line() +
  facet_wrap(.~ population, scales = "free") + 
  scale_y_continuous(limits = c(0, 100))


HCVliving <- df_allpop%>%ungroup()%>%mutate(year = rep(seq(2015, (2015 + 98),1 ), each = 420))%>%
  filter(!cascade %in% c("s", "cured"))%>%filter(year == 2020)%>%
  group_by(time, Var1)%>%mutate(best = sum(Freq))%>%filter(year == 2020)

HCVliving_ab <- df_allpop%>%ungroup()%>%mutate(year = rep(seq(2015, (2015 + 98),1 ), each = 420))%>%
  filter(cascade %in% c("diag_ab"))%>%
  group_by(time, Var1)%>%mutate(best = sum(Freq))%>%filter(year == 2020)
  

HCVliving_RNA <- df_allpop%>%ungroup()%>%mutate(year = rep(seq(2015, (2015 + 98),1 ), each = 420))%>%
  filter(cascade %in% c("diag_RNA"))%>%
  group_by(time, Var1)%>%mutate(best = sum(Freq))%>%filter(year == 2020)

HCVliving_T <- df_allpop%>%ungroup()%>%mutate(year = rep(seq(2015, (2015 + 98),1 ), each = 420))%>%
  filter(cascade %in% c("treat"))%>%
  group_by(time, Var1)%>%mutate(best = sum(Freq))%>%filter(year == 2020)

HCV_state <- cbind(year = HCVliving_ab$time, 
      pop = HCVliving$Var1, 
      livingHCV = round(HCVliving$best, digits = 1), 
      ab = round(HCVliving_ab$best, digits = 1), 
      RNA = round(HCVliving_RNA$best, digits = 1), 
      Tinit = round(HCVliving_T$best,digits = 1)
      )
```



## Population size 
```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 9, fig.width = 12, fig.cap = "data points: estimated" }
ggpubr::ggarrange(plotlist = subpop_N_plot)  + 
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm")) 

``` 

## HCV seroprevalence & RNA prevalence 
### data points
  - C_PWID: ANSPS
  - C_fPWID: National program baseline 
  - P_PWID: AUSHEP
  - P_fPWID: AUSHEP
  - P_nPWID: AUSHEP
  - Prison: AUSHEP

```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 9, fig.width = 12, fig.cap = "" }
popPrevPlot
popPrevRNAPlot
settingPrevPlot
settingPrevRNAPlot
``` 

## HCV incidence  
### data points
  - C_PWID: 
  - C_fPWID: 
  - P_PWID: SToP-C 
  - P_fPWID: SToP-C 
  - P_nPWID: SToP-C 
  - Prison: SToP-C 

```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 9, fig.width = 12, fig.cap = "" }
popIncPlot
settingIncPlot
``` 

## HCV primary infection 
### data points
  - C_PWID: ANSPS
  - C_fPWID: 
  - P_PWID: SToP-C 
  - P_fPWID: SToP-C 
  - P_nPWID: SToP-C 
  - Prison: SToP-C 
<details>
  <summary>HCV primary infection</summary>
    ```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
   popIncpPlot
    ```
</details> 

## HCV reinfection 
### data points
  - C_PWID: 
  - C_fPWID: 
  - P_PWID: SToP-C 
  - P_fPWID: SToP-C 
  - P_nPWID: SToP-C 
  - Prison: SToP-C 
<details>
  <summary>HCV re-infection</summary>
    ```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
   popIncrePlot
    ```
</details> 


## Cascade [monthly coverage]
### data points
- testing
  - C_PWID: national program baseline
  - C_fPWID: national program baseline
  - P_PWID: AUSHEP
  - P_fPWID: AUSHEP
  - P_nPWID: AUSHEP 
- treatment initiation coverage 
  - C_PWID: 
  - C_fPWID: 
  - P_PWID: Pivot
  - P_fPWID: 
  - P_nPWID: 

```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 9, fig.width = 12, fig.cap = "" }
P_abFrac
P_RNAFrac
P_RNAonlyFrac
P_TinitFrac
``` 

## Treatment 

- Number of treatment initiation 
  - Community   
  - Prison: National number of treatment initiated * the percentage of treatment initiated in prison [from Cascade report]
  
- Prevalence of recent treatment  
data points
  - C_PWID: 
  - C_fPWID: 
  - P_PWID: AUSHEP
  - P_fPWID: AUSHEP
  - P_nPWID:   
*calulation: number of initiated treatment in the previosu year/ total number of subpop  



  <details>
    <summary>Number of treatment initiation  </summary>
```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
   N_treatment_setting_p
```
  </details> 


  <details>
    <summary>Prevalence of recent treatment</summary>
    ```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
   treatrecentPrev_p 
    ```
  </details> 


```{r, message=FALSE, warning=FALSE, echo=FALSE}
beta_varying <- matrix(0, nrow = 2, ncol = POC_AU$npops)

beta_varying[1, ] <- c(best_estimates$beta1[1], best_estimates$beta2[1],
                       best_estimates$beta3[1],best_estimates$beta4[1],
                       best_estimates$beta5[1])
beta_varying[2, ] <- c(bvalue)

colnames(beta_varying) <- POC_AU$popNames
rownames(beta_varying) <- c(2015, 2019)

eta_varying <- matrix(0, nrow = 2, ncol = POC_AU$npops)
eta_varying[1, ] <- c(dfList$eta[, 2,1])
eta_varying[2, ] <- c(TreatInit)
colnames(eta_varying) <- POC_AU$popNames
rownames(eta_varying) <- c(2015, 2019)

colnames(pop_array[ , ,1]) <- POC_AU$popNames
rownames(pop_array[ , ,1]) <- POC_AU$popNames


```






  
<details>
  <summary>initial prevalence </summary>
```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
knitr::kable(best_estimates[1, c(44:48)])
```
</details>   
  
<details>
  <summary>population transition</summary>
```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
knitr::kable(pop_array[, , 1])
```
</details> 
  
  
<details>
  <summary>treatment initiation </summary>
```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
knitr::kable(eta_varying)
```
</details> 

<details>
  <summary>beta value </summary>
```{r, echo=FALSE, warning=FALSE, message=FALSE, eval=TRUE}
knitr::kable(beta_varying) 
```
</details> 