---
title: "Calibration: population"
author: "Joyce Wu"
date: "09/06/2023"
output: word_document
---

```{r message=FALSE, warning=FALSE, echo=FALSE, include=FALSE}
# this script is for visulizing the calibraiton outcomes 

rm(list = ls())

library(ggplot2)
library(ggrepel)
library(directlabels)
library(gridExtra)
library(grid)

project_name <- "POC_AU"

codefun_path <- paste("/Users/jjwu/Documents/Simplified-HCV-testing-model")

data_path <- paste("/Users/jjwu/Library/CloudStorage/OneDrive-UNSW/05. PhD Project/Simplified HCV testing model_/Projects/", 
                   project_name, sep = "")
# Load useful libraries

library("readr")
library("dplyr")
library("tidyr")
library("purrr")
library("parallel")
library("pacman")
library("doMC")

Rcode <- file.path(codefun_path, "03. Code")

DataFolder <- file.path(data_path, "01. DATA/model input" )

OutputFolder <- file.path(data_path, "02. Output")

load(file.path(OutputFolder, paste0(project_name, ".rda")))

load(file.path(OutputFolder, paste0(project_name, "cali_init", ".rda")))

source(file.path(Rcode, "/Functions/plotFunctions.R")) 

# setting end Year 

endY <- 100

```

```{r echo=FALSE, include=FALSE}
#### N: each subpop/ total  #### 
# subpop as list
subpop_N <- lapply(POC_AU$popNames, function(x){ 
  
  a <- popResults_MidYear(POC_AU, calibrateInit,
                          Population = x,
                          Disease_prog = NULL, 
                          Cascade = NULL, param = NULL, 
                          endYear = endY)%>%ungroup()
})

names(subpop_N) <- POC_AU$popNames

# all subpop in one list 
pop_N <- dplyr::bind_rows(subpop_N, .id = 'population')

# total number 

total_N <- pop_N%>%group_by(year)%>%summarise(best = sum(best))

#### N: community ####
commu_N <- popResults_MidYear(POC_AU, calibrateInit,
                              Population = c("C_PWID", "C_fPWID"),
                              Disease_prog = NULL, 
                              Cascade = NULL, param = NULL, 
                              endYear = endY)%>%ungroup()%>%
  dplyr::group_by(year)%>%summarise_at("best",sum)

#### N: prison ####
prison_N <- popResults_MidYear(POC_AU, calibrateInit,
                               Population = c("P_PWID", "P_fPWID", "P_nPWID"),
                               Disease_prog = NULL, 
                               Cascade = NULL, param = NULL, 
                               endYear = endY)%>%ungroup()%>%
  dplyr::group_by(year)%>%summarise_at("best",sum)

#### %: PWID in community/prison ####
commu_proP <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                    as.data.frame(pop_N[pop_N$population =="C_PWID",3] / commu_N[ ,-1])*100)%>%
  tibble::as_tibble()

prison_proP <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                     as.data.frame(pop_N[pop_N$population =="P_PWID",3] / prison_N[ ,-1])*100)%>%
  tibble::as_tibble()

#### % fPWID in prison #### 
prison_profP <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                      as.data.frame(pop_N[pop_N$population =="P_fPWID",3] / prison_N[ ,-1])*100)%>%
  tibble::as_tibble()



#### number of annual leaving in each subpop ####
# this is for getting annual number of released in non-PWID in prison 
rel <- indicatorResult_uno(POC_AU, calibrateInit, "newLeave",
                           populations = POC_AU$popNames, endYear= endY)%>%
  mutate(year = year + POC_AU$cabY - 1) 

#### number of annual entry model in each subpop ####
# to get the annual number of incarceration in non-PWID in prison 
entry <- indicatorResult_uno(POC_AU, calibrateInit, "newEntry",
                             populations = POC_AU$popNames, endYear= endY) %>%
  mutate(year = year + POC_AU$cabY - 1)



#### annual number of incarceration/release/injection relapse/ stopping injection #### 

PopTransition <- as.data.frame.table(calibrateInit$newpop_tran)%>%
  mutate(timestep = c(rep(seq(POC_AU$startYear, endY-POC_AU$timestep,
                              POC_AU$timestep),each = POC_AU$npops*POC_AU$npops)),
         from = Var1,
         To = Var2)%>%select(-c(Var1, Var2, Var3))
# giving the average number to first time step 
impute <- PopTransition%>%filter(timestep >1 &timestep <2)%>%
  group_by(from, To)%>%
  mutate(total_pop = sum(Freq)/length(Freq))%>%
  select(total_pop)%>%ungroup()

impute <- impute[c(1:as.numeric(POC_AU$npops*POC_AU$npops)),]

PopTransition[c(1:as.numeric(POC_AU$npops*POC_AU$npops)), "Freq"] <- impute$total_pop 

PopTransition_all <- cbind.data.frame(timestep = PopTransition$timestep, 
                                      from = PopTransition$from,  
                                      to = PopTransition$To, 
                                      best = PopTransition$Freq)%>%
  as_tibble()%>%
  mutate(year = rep(rep(seq(1, 100-1,1),each = 1/POC_AU$timestep),
                    each = POC_AU$npops*POC_AU$npops))

PPTranTo <- PopTransition_all%>%
  group_by(year, from, to)%>%summarise_at(.vars = "best", sum)

# incarceration 
incarce <- list()

incarce[["PWID"]] <- PPTranTo%>%filter(from == "C_PWID" & to == "P_PWID")

incarce[["fPWID"]] <- PPTranTo%>%filter(from == "C_fPWID" & to == "P_fPWID")

incarce_bind <- dplyr::bind_rows(incarce, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()%>%
  select(year, population, best)

entry_nonPWID <- entry%>%filter(population =="P_nPWID") 

# total incarceration = incarceration in C_PWID + incarceration in C_fPWID + incarceration in non-PWID (entry:non-PWID)
incar_total <- rbind(incarce_bind, entry_nonPWID)%>%group_by(year)%>%
  summarize(best = sum(best))

# release 
release <- list()

release[["PWID"]] <- PPTranTo%>%filter(from == "P_PWID" & to == "C_PWID")

release[["fPWID"]] <- PPTranTo%>%filter(from == "P_fPWID" & to == "C_fPWID")

release_bind <- dplyr::bind_rows(release, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()%>%select(year, population, best)

release_nonPWID <- rel%>%filter(population =="P_nPWID") 

release_total <- rbind(release_bind, release_nonPWID)%>%group_by(year)%>%
  summarize(best = sum(best))

# injection relapse 
inj_relap <- list()

inj_relap[["community"]] <- PPTranTo%>%filter(from == "C_fPWID" & to == "C_PWID")

inj_relap[["prison"]] <- PPTranTo%>%filter(from == "P_fPWID" & to == "P_PWID")

inj_relap_bind <- dplyr::bind_rows(inj_relap, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()


# stopping injection 
inj_stop <- list()

inj_stop[["community"]] <- PPTranTo%>%filter(from == "C_PWID" & to == "C_fPWID")

inj_stop[["prison"]] <- PPTranTo%>%filter(from == "P_PWID" & to == "P_fPWID")

inj_stop_bind <- dplyr::bind_rows(inj_stop, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()



####  incidence of stopping injecting #### 
inj_stop_inc <- list()

inj_stop_inc[["community"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(inj_stop[["community"]][ , "best"] / 
                        subpop_N[["C_PWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

inj_stop_inc[["prison"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(inj_stop[["prison"]][ , "best"] / 
                        subpop_N[["P_PWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

inj_stop_inc_bind <- dplyr::bind_rows(inj_stop_inc, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()
####  incidence of injection relapse #### 
inj_relap_inc <- list()

inj_relap_inc[["community"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(inj_relap[["community"]][ , "best"] / 
                        subpop_N[["C_fPWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

inj_relap_inc[["prison"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(inj_relap[["prison"]][ , "best"] / 
                        subpop_N[["P_fPWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

inj_relap_inc_bind <- dplyr::bind_rows(inj_relap_inc, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()

#### incidence of incarceration  ####
incar_inc <- list()

incar_inc[["PWID"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                    as.data.frame(incarce[["PWID"]][ , "best"] / 
                                    subpop_N[["C_PWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

incar_inc[["fPWID"]] <- cbind(year = seq(POC_AU$startYear , endY-1 ,1),
                             as.data.frame(incarce[["fPWID"]][ , "best"] / 
                                             subpop_N[["C_fPWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

incar_inc_bind <- dplyr::bind_rows(incar_inc, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()

#### incidence of release  ####
release_inc <- list()

release_inc[["PWID"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(release[["PWID"]][ , "best"] / 
                        subpop_N[["P_PWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

release_inc[["fPWID"]] <- 
  cbind(year = seq(POC_AU$startYear , endY-1 ,1),
        as.data.frame(release[["fPWID"]][ , "best"] /
                        subpop_N[["P_fPWID"]][ ,"best"])*100)%>%
  tibble::as_tibble()

release_inc_bind <- dplyr::bind_rows(release_inc, .id = 'population')%>%
  mutate(year = POC_AU$cabY + year - 1)%>%ungroup()
#### tidy up datapoint #### 

datapoint <- list()
datapoint[["N"]] <- 
  cbind.data.frame(year = rep(POC_AU$simY, length(POC_AU$popNames) +3), 
                   indicator = c(POC_AU$popNames, "Community", "Prison", "Total"), 
                   realpop = c(80000, 400000, NA, NA, NA, 480000, 40000, 520000),
                   low= c(60000, 30000, NA, NA, NA, 360000, NA, NA),
                   up = c(100000, 600000, NA, NA, NA, 700000, NA, NA))

datapoint[["frac"]] <- 
  cbind.data.frame(year = rep(POC_AU$simY, 3), 
                   indicator = c("commu_proP_fit", "prison_proP_fit", 
                                 "prison_profP_fit"), 
                   realpop = c(16.67, 16.12, 35.88),
                   low= c(NA, NA, NA),
                   up = c(NA, NA, NA))

datapoint[["flow"]] <- 
  cbind.data.frame(year = rep(POC_AU$simY, 3), 
                   indicator = c("incar", "release", 
                                  "commu_stopinj"), 
                   realpop = c(63753, 63113, 5.4),
                   low= c(NA, NA, 4.3),
                   up = c(NA, NA, 6.7))

#==============================================================================#

```

```{r echo=FALSE, include=FALSE}
####plot: number of total pop  ####

totalPop_plot <- indicatorPlot(POC_AU, total_N, 
              ylabel = "Number",
              xlimits = c(POC_AU$startYear, 
                          POC_AU$startYear+30, 5),
              calibration_Y = POC_AU$cabY,
              rangeun = NULL, 
              groupPlot = NULL, 
              facetPlot = NULL,
              observationData = NULL, 
              simulateYear = NULL) + theme_bw() +
  scale_y_continuous(limits = c(515000,525000)) + 
  ggtitle("Number of total population") + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Total", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), 
             colour = "black") 
####plot: number of pop in community/prison   ####
commuPop_plot <- indicatorPlot(POC_AU, commu_N, 
                          ylabel = "Number",
                          xlimits = c(POC_AU$startYear, 
                                      POC_AU$startYear+30, 5),
                          calibration_Y = POC_AU$cabY,
                          rangeun = NULL, 
                          groupPlot = NULL, 
                          facetPlot = NULL,
                          observationData = NULL, 
                          simulateYear = NULL) + theme_bw() +
  ggtitle("Number of population in community") + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Community", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), 
    colour = "black") + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Community", "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Community", "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1))) + 
  scale_y_continuous(limits = c(0,750000), breaks = seq(0, 750000, 50000)) 
  
prisonPop_plot <- indicatorPlot(POC_AU, prison_N, 
                               ylabel = "Number",
                               xlimits = c(POC_AU$startYear, 
                                           POC_AU$startYear+30, 5),
                               calibration_Y = POC_AU$cabY,
                               rangeun = NULL, 
                               groupPlot = NULL, 
                               facetPlot = NULL,
                               observationData = NULL, 
                               simulateYear = NULL) + theme_bw() +
  ggtitle("Number of population in prisons") + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Prison", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), 
    colour = "black") + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Prison", "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == "Prison", "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1))) + 
  scale_y_continuous(limits = c(0,50000), breaks = seq(0, 50000, 5000))

####plot: number of subpop   ####
# sub pop full names 
Namelab <- c("PWID in community", "former PWID in community",
             "PWID in prison", "former PWID in prison", "non-PWID in prison")

subpop_N_plot <- list() 

for(x in seq_along(names(subpop_N))){ 
  
  subpop_N_plot[[x]] <- indicatorPlot(POC_AU, subpop_N[[x]] , 
                                      ylabel = "Number",
                                      xlimits = c(POC_AU$startYear, 
                                                  POC_AU$startYear+30, 5),
                                      calibration_Y = POC_AU$cabY,
                                      rangeun = NULL, 
                                      groupPlot = NULL, 
                                      facetPlot = NULL,
                                      observationData = NULL, 
                                      simulateYear = NULL) +
    theme_bw() + ggtitle(paste0(Namelab[x])) 
    
}

subpop_N_plot[[1]] <- subpop_N_plot[[1]] + 
  scale_y_continuous(limits = c(0, 110000), breaks = seq(0, 110000, 5000)) + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[1], "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black") + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[1], "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[1], "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))

subpop_N_plot[[2]] <- subpop_N_plot[[2]] + 
  scale_y_continuous(limits = c(0, 700000), breaks = seq(0, 700000, 50000)) + 
  
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[2], "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black") + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[2], "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[2], "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))

subpop_N_plot[[3]] <- subpop_N_plot[[3]] + 
  scale_y_continuous(limits = c(0, 8000), breaks = seq(0, 8000, 500)) + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[3], "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black") + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[3], "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[3], "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))
  

subpop_N_plot[[4]] <- subpop_N_plot[[4]] + 
  scale_y_continuous(limits = c(0, 20000), breaks = seq(0, 20000, 1000)) + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[4], "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black") + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[4], "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[4], "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))

subpop_N_plot[[5]] <- subpop_N_plot[[5]] + 
  scale_y_continuous(limits = c(0, 25000), breaks = seq(0, 25000, 1000)) + 
  geom_point(aes(
    y=datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[5], "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black") + 
  geom_segment(
    aes(y = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[5], "low"], 
        yend = datapoint[["N"]][datapoint[["N"]][, "indicator"] == names(subpop_N)[5], "up"], 
        x = (POC_AU$simY - POC_AU$cabY + 1) , xend = (POC_AU$simY - POC_AU$cabY + 1)))



####plot: % of PWID/fPWID in community/prison  ####
# P_PWID 
frac_PPWID_plot <- indicatorPlot(POC_AU, prison_proP , 
                                 ylabel = "Percentage (%)",
                                 xlimits = c(POC_AU$startYear, 
                                             POC_AU$startYear+30, 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeun = NULL, 
                                 groupPlot = NULL, 
                                 facetPlot = NULL,
                                 observationData = NULL, 
                                 simulateYear = NULL) + 
  theme_bw() + 
  scale_y_continuous(limits = c(0,20), breaks = seq(0, 20,1)) + ggtitle("PWID in prison") + 
  geom_point(aes(
    y=datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "prison_proP_fit", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black") 
  
# P_fPWID
frac_PfPWID_plot <- indicatorPlot(POC_AU, prison_profP , 
                                 ylabel = "Percentage (%)",
                                 xlimits = c(POC_AU$startYear, 
                                             POC_AU$startYear+30, 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeun = NULL, 
                                 groupPlot = NULL, 
                                 facetPlot = NULL,
                                 observationData = NULL, 
                                 simulateYear = NULL) + 
  theme_bw() + 
  scale_y_continuous(limits = c(0,40), breaks = seq(0, 40,5)) + ggtitle("Former PWID in prison") + 
  geom_point(aes(
    y=datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "prison_profP_fit", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black") 

# C_PWID 
frac_CPWID_plot <- indicatorPlot(POC_AU, commu_proP , 
                                  ylabel = "Percentage (%)",
                                  xlimits = c(POC_AU$startYear, 
                                              POC_AU$startYear+30, 5),
                                  calibration_Y = POC_AU$cabY,
                                  rangeun = NULL, 
                                  groupPlot = NULL, 
                                  facetPlot = NULL,
                                  observationData = NULL, 
                                  simulateYear = NULL) + 
  theme_bw() + 
  scale_y_continuous(limits = c(0,20), breaks = seq(0, 20,1)) + ggtitle("PWID in community") + 
  geom_point(aes(
    y=datapoint[["frac"]][datapoint[["frac"]][, "indicator"] == "commu_proP_fit", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), colour = "black") 

####plot: annual number entry to/release from prisons #### 
New_incar_plot <-  indicatorPlot(POC_AU, incar_total,
              ylabel = "Number",
              xlimits = c(POC_AU$cabY,
                          POC_AU$cabY+30, 5),
              calibration_Y = POC_AU$cabY,
              rangeu = NULL,
              groupPlot = NULL,
              facetPlot = NULL,
              observationData = NULL, 
              simulateYear = NULL) +
  ggtitle("Annual number entry prisons") + theme_bw() + 
  scale_y_continuous(limits = c(0, 65000), breaks = seq(0, 65000, 5000)) + 
  geom_point(aes(
    y=datapoint[["flow"]][datapoint[["flow"]][, "indicator"] == "incar", "realpop"], 
    x = POC_AU$simY ), colour = "black")

New_release_plot <-  indicatorPlot(POC_AU, release_total,
                                 ylabel = "Number",
                                 xlimits = c(POC_AU$cabY,
                                             POC_AU$cabY+30, 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeu = NULL,
                                 groupPlot = NULL,
                                 facetPlot = NULL,
                                 observationData = NULL, 
                                 simulateYear = NULL) +
  ggtitle("Annual number release from prisons") + theme_bw() + 
  scale_y_continuous(limits = c(0, 65000), breaks = seq(0, 65000, 5000)) + 
  geom_point(aes(
    y=datapoint[["flow"]][datapoint[["flow"]][, "indicator"] == "release", "realpop"], 
    x = POC_AU$simY ), colour = "black")

####plot: annual number stopping/relapse injection ####
# stopping injection
New_stopinj_plot <-  indicatorPlot(POC_AU, inj_stop_bind,
                                 ylabel = "Number",
                                 xlimits = c(POC_AU$cabY,
                                             POC_AU$cabY+30, 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeu = NULL,
                                 groupPlot = NULL,
                                 facetPlot = population,
                                 observationData = NULL, 
                                 simulateYear = NULL) +
  ggtitle("Annual number stop injection") + theme_bw() + 
  scale_y_continuous(limits = c(0, 10000), breaks = seq(0, 10000, 1000)) 
# relapse injection
New_relapinj_plot <-  indicatorPlot(POC_AU, inj_relap_bind,
                                   ylabel = "Number",
                                   xlimits = c(POC_AU$cabY,
                                               POC_AU$cabY+30, 5),
                                   calibration_Y = POC_AU$cabY,
                                   rangeu = NULL,
                                   groupPlot = NULL,
                                   facetPlot = population,
                                   observationData = NULL, 
                                   simulateYear = NULL) +
  ggtitle("Annual number relapse injection") + theme_bw() + 
  scale_y_continuous(limits = c(0, 5000), breaks = seq(0, 5000, 500)) 

##============================================================================##







####plot: incidence of entry to/release from prisons #### 
Inc_incar_plot <- indicatorPlot(POC_AU,incar_inc_bind ,
                                 ylabel = "Incidence",
                                 xlimits = c(POC_AU$cabY,
                                             POC_AU$cabY+30, 5),
                                 calibration_Y = POC_AU$cabY,
                                 rangeu = NULL,
                                 groupPlot = NULL,
                                 facetPlot = population,
                                 observationData = NULL, 
                                 simulateYear = NULL) +
  ggtitle("Incidence of incarceration") + theme_bw() + 
  scale_y_continuous(limits = c(0, 20), breaks = seq(0, 20, 1)) 

Inc_release_plot <-  indicatorPlot(POC_AU, release_inc_bind,
                                   ylabel = "Incidence",
                                   xlimits = c(POC_AU$cabY,
                                               POC_AU$cabY+30, 5),
                                   calibration_Y = POC_AU$cabY,
                                   rangeu = NULL,
                                   groupPlot = NULL,
                                   facetPlot = population,
                                   observationData = NULL, 
                                   simulateYear = NULL) +
  ggtitle("Incidence of released") + theme_bw() + 
  scale_y_continuous(limits = c(0, 200), breaks = seq(0, 200, 10)) 

####plot: incidence of stopping/relapse injection ####
# stopping injection
Inc_stopinj_plot <- list()

inj_stop_inc_bind[[1]]
Inc_stopinj_plot <- lapply(inj_stop_inc, function(x){ 
  
  a <- indicatorPlot(POC_AU, x,
                     ylabel = "Incidence",
                     xlimits = c(POC_AU$startYear ,
                                 POC_AU$startYear+30, 5),
                     calibration_Y = POC_AU$cabY,
                     rangeu = NULL,
                     groupPlot = NULL,
                     facetPlot = NULL,
                     observationData = NULL, 
                     simulateYear = NULL) +
    ggtitle("Incidence of stop injection") + theme_bw() + 
    scale_y_continuous(limits = c(0, 120), breaks = seq(0, 120, 5))
  
  
  
  return(a)
   
})

Inc_stopinj_plot[["community"]] <-  Inc_stopinj_plot[["community"]] + 
  geom_point(aes(
    y=datapoint[["flow"]][datapoint[["flow"]][, "indicator"] == "commu_stopinj", "realpop"], 
    x = POC_AU$simY - POC_AU$cabY + 1 ), 
    colour = "black") + 
    geom_segment(
      aes(y = datapoint[["flow"]][datapoint[["flow"]][, "indicator"] == "commu_stopinj", "low"], 
          yend = datapoint[["flow"]][datapoint[["flow"]][, "indicator"] == "commu_stopinj", "up"], 
          x = POC_AU$simY - POC_AU$cabY + 1, xend = POC_AU$simY - POC_AU$cabY + 1 )) + 
  scale_y_continuous(limits = c(0,20), breaks = seq(0, 20, 1))

  
  
# relapse injection
Inc_relapinj_plot <-  indicatorPlot(POC_AU, inj_relap_inc_bind,
                                    ylabel = "Incidence",
                                    xlimits = c(POC_AU$cabY,
                                                POC_AU$cabY+30, 5),
                                    calibration_Y = POC_AU$cabY,
                                    rangeu = NULL,
                                    groupPlot = NULL,
                                    facetPlot = population,
                                    observationData = NULL, 
                                    simulateYear = NULL) +
  ggtitle("Incidence of relapse injection") + theme_bw() + 
  scale_y_continuous(limits = c(0, 20), breaks = seq(0, 20, 1))





```
## Calibration of population size, population transition
 
(1) Number of total population (Figure 1.)
(2) Number of population size in community/prisons (Figure 2.)
(3) Number of population size in each sub-population (Figure 3.)
(4) Fraction of PWID/former PWID in community/prisons (Figure 4.)
(5) Annual number of stop/relapse injection in community/prisons (Figure 5.)
(6) Annual number of incarceration/release in PWID/former PWID (Figure 6.)   
(7) Incidence of stop injection in community/prisons (Figure 7. )
(8) Incidence of relapse injection in community/prisons  (Figure 8. )
(9) Incidence of stopping injection in community/prisons (Figure 9. )
The blue lines are model outputs and black dots and lines represent the data points from in all figures. 

\newpage

## Figure1. number of population 
```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 6, fig.width = 8, fig.cap = "" }
ggpubr::ggarrange(totalPop_plot, nrow = 1) + 
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm")) 

```

\newpage
## Figure2. number of population size in community/prisons
```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 6, fig.width = 8, fig.cap = "" }
ggpubr::ggarrange(commuPop_plot,prisonPop_plot) + 
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm")) 

```

\newpage
## Figure3. number of population size in each sup-population  
```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 8, fig.width = 12, fig.cap = "" }
ggpubr::ggarrange(subpop_N_plot[[1]], subpop_N_plot[[2]], 
                  subpop_N_plot[[3]],subpop_N_plot[[4]], 
                  subpop_N_plot[[5]]) + 
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm")) 

```
 

\newpage
## Figure4. Fraction of PWID/former PWID in community/prisons 
$${Fraction of PWID\_setting =
\frac{PWID\_setting}{N\_setting}*100}$$

$${Fraction of former PWID\_prison =
\frac{formerPWID\_prison}{N\_prison}*100}$$
```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 9, fig.width = 12, fig.cap = "Figure 9." }
ggpubr::ggarrange(frac_CPWID_plot, frac_PPWID_plot, frac_PfPWID_plot) + 
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm")) 

``` 

\newpage

## Figure5. Annual number of stop/relapse injection in community/prisons 
```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 9, fig.width = 12, fig.cap = "" }
ggpubr::ggarrange(New_stopinj_plot, New_relapinj_plot) + 
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm")) 

``` 

\newpage

## Figure6. Annual number of incarceration/release in PWID and former PWID  
```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 9, fig.width = 12, fig.cap = "" }
ggpubr::ggarrange(New_incar_plot, New_release_plot) + 
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm")) 

``` 

\newpage

## Figure7. Incidence of stop injection in community/prisons 
Incidence of stop injection in {`setting`} = annual number of stopping injection in {`setting`}/Number of PWID in {`setting`}*100
```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 9, fig.width = 12, fig.cap = "" }
ggpubr::ggarrange(Inc_stopinj_plot[["community"]],Inc_stopinj_plot[["prison"]] ) + 
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm")) 

``` 

\newpage
## Figure8. Incidence of relapse injection in community/prisons 
Incidence of relapse injection in {`setting`} = annual number of relapse injection in {`setting`}/Number of former PWID in {`setting`}*100 
```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 9, fig.width = 12, fig.cap = "" }
ggpubr::ggarrange(Inc_relapinj_plot) + 
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm")) 

``` 


                  
## Figure9. Incidence of incarceration/release in PWID and former PWID  
Incidence of incarceration in {`population`} = annual number of incarceration in {`population`}/Number of {`population`} in community *100 
Incidence of release in {`population`} = annual number of release in {`population`}/Number of {`population`} in prisons*100 

```{r echo=FALSE, warning=FALSE, message=FALSE,  fig.height= 9, fig.width = 12, fig.cap = "" }
ggpubr::ggarrange(New_incar_plot, New_release_plot) + 
  theme(plot.margin = margin(0.1,0.1,0.1,0.1, "cm")) 

``` 


